Presentation Title

### 2017-04-12 chapters/ch2-checkpoint.tex
Prepare for tomorrow's presentation

\item A block of type $\gamma$ is a five-tuple, i.e.
  $$c_{i,j} = (\texttt{h}(b_{i,j}), H(\mathcal{C}_r), r, p, s)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round, finally $s$ is a signature of the block.

@@

\begin{lemma}
  Consensus phase satisfied agreement, total order and liveness.
\end{lemma}
\begin{proof}
  Defer proof? Refer to the papers.
\end{proof}

\begin{theorem}
  Checkpoint consensus satisfied agreement, total order and liveness.
\end{theorem}
\begin{proof}
  (sketch) Both phases are asynchronous so we do not need to make assumptions on
  when begin phase begins. Both phases also satisfy the agreement, total order
  and liveness.
\end{proof}

>>>>

% TODO remove the p indication
\item A block of type $\gamma$ is a six-tuple, i.e.
  $$c_{i,j} = (\texttt{h}(b_{i,j-1}), \texttt{h}(\mathcal{C}_r), h, r, p, s)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round, finally $s$ is a signature of the block.

@@

\begin{lemma}
  Consensus phase satisfies agreement, total order and liveness.
\end{lemma}
\begin{proof}
  Defer proof? Refer to the papers.
\end{proof}

\begin{theorem}
  Checkpoint consensus satisfies agreement, total order and liveness.
\end{theorem}
\begin{proof}
  (sketch) Both phases are asynchronous so we do not need to make assumptions on
  when begin phase begins. Both phases also satisfy the agreement, total order
  and liveness.
\end{proof}

### 2017-04-12 presentation.tex
Prepare for tomorrow's presentation

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-bad-cp}
  \centering
  \caption{CP block is a five-tuple: $c_{i,j} = (\texttt{h}(b_{i,j-1}),
    \texttt{h}(\mathcal{C}_r), r, p, s)$, $\mathcal{C}_r$ is the consensus
    result at round $r$, $p =$ promoter indicator, $s =$ signature.}
  \end{figure}

@@

\subsection{Implementation}
\begin{frame}{Implementation}
  \begin{itemize}
    \item Currently on going---using Python and Twisted
    \item Completed BFT consensus algorithm
    \item Completed local TrustChain with Checkpoints
    \item Next step is networked TrustChain and validation protocol
  \end{itemize}
\end{frame}
\end{document}

>>>>

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-bad-cp}
  \centering
  \caption{CP block is a six-tuple: $c_{i,j} = (\texttt{h}(b_{i,j-1}),
    \texttt{h}(\mathcal{C}_r), h, r, p, s)$, $\mathcal{C}_r$ is the consensus
    result at round $r$, $p =$ promoter indicator, $s =$ signature.}
  \end{figure}

@@

\subsection{Implementation and Experimentation Results}
\begin{frame}{Implementation (4 weeks ago)}
  \begin{itemize}
    \item Currently on going---using Python and Twisted
    \item Completed BFT consensus algorithm
    \item Completed local TrustChain with Checkpoints
    \item Next step is networked TrustChain and validation protocol
  \end{itemize}
\end{frame}

\begin{frame}{Implementation}
  \begin{itemize}
    \item Completed BFT consensus algorithm, with erasure coding
    \item Completed TrustChain with Checkpoints, with experiments on DAS5
    \item Validation function is working
    \item Next step is to build validation into a network protocol and do experiments
  \end{itemize}
\end{frame}

\begin{frame}{Experiment with 500 nodes---no gossip}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{figures/consensus-500-no-gossip}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Experiment with 500 nodes---with gossip}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{figures/consensus-500}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Experiment with 500 nodes---with gossip}
  \begin{block}{Conclusion}
    \begin{itemize}
      \item The number of facilitators affects the consensus latency ($O(N\log{N})$?).
      \item The transaction rate has little or not effect on the average consensus latency.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Planned experiments}
  \begin{itemize}
    \item Consensus latency (y-axis) vs population size (x-axis)---to
      investigate how population size impacts consensus latency.
    \item Global transaction rate vs population size---to investigate
      the scalability property.
    \item Global validation rate vs population size---to also investigate the
      scalability property.
  \end{itemize}
\end{frame}
\end{document}
